\thesistitle

### 2019-07-16 sections/clonerefactor.tex
Remove existing

\begin{equation}\label{eq:subset}
C_1 \subseteq C_2 \iff \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
\end{equation}

@@

\begin{equation}\label{eq:removeall}
\text{For each new clone }C_{new}\text{ found, only add it to }S \text{ iff } (C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S)
\end{equation}

>>>>

\begin{equation}\label{eq:subset}
C_1 \subseteq C_2 \Leftrightarrow \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
\end{equation}

@@

\begin{equation}\label{eq:removeexisting}
(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) \neq \emptyset \Rightarrow S = S \cup C_{new}
\end{equation}
